### 2020-02-28 ncov.tex
..
update

@@

Since December 2019, a novel coronavirus (SARS-CoV-2) has been spreading in China and other parts of the world \citep{pneumonia}.
Although the virus is believed to have originated from animal reservoirs \citep{cdcncov}, the ability of SARS-CoV-2 ability to directly transmit between humans has posed a greater threat for its spread \citep{huang2020clinical,who26report}.
As of February 26, 2020, the World Health Organization (WHO) has confirmed 81,109 cases, including 2,918 confirmed cases in 37 different countries, outside China \citep{who37report}.
% Also on January 30, 2020, WHO declared the outbreak a Public Health Emergency of International Concern \citep{whoemer}.

@@

Estimating the basic reproductive number \Ro is crucial for predicting the course of an outbreak and planning intervention strategies.
Here, we use a gamma approximation \citep{park2019practical} to decompose \Ro estimates into three key quantities ($r$, $\bar G$, and $\kappa$) and apply a multilevel Bayesian framework to compare estimates of \Ro for the novel coronavirus outbreak.
Our results demonstrate the importance of accounting for uncertainties associated with the underlying generation-interval distributions, including uncertainties in the amount of dispersion in the generation intervals.
Our analysis of individual studies shows that many early estimates of \Ro rely on overly strong assumptions.

@@

\section*{Declaration of interests}

>>>>

\section*{Keywords}

SARS-CoV-2, COVID-19, novel coronavirus, basic reproductive number, generation interval, Bayesian multilevel model

@@

Since December 2019, a novel coronavirus (SARS-CoV-2) has been spreading in China and other parts of the world \citep{pneumonia}.
Although the virus is believed to have originated from animal reservoirs \citep{cdcncov}, the ability of SARS-CoV-2 ability to directly transmit between humans has posed a greater threat for its spread \citep{huang2020clinical,who26report}.
As of February 27, 2020, the World Health Organization (WHO) has confirmed 82,294 cases of the coronavirus disease (COVID-19), including 3,664 confirmed cases in 46 different countries, outside China \citep{who38report}.
% Also on January 30, 2020, WHO declared the outbreak a Public Health Emergency of International Concern \citep{whoemer}.

@@

Estimating the basic reproductive number \Ro is crucial for predicting the course of an outbreak and planning intervention strategies.
Here, we use a gamma approximation \citep{park2019practical} to decompose \Ro estimates into three key quantities ($r$, $\bar G$, and $\kappa$) and apply a multilevel Bayesian framework to compare estimates of \Ro for the novel coronavirus outbreak.
Our results demonstrate the importance of accounting for uncertainties associated with the underlying generation-interval distributions, including uncertainties in the amount of dispersion in the generation intervals.
Our analysis of individual studies shows that many early estimates of \Ro rely on strong assumptions.

@@

\section*{Competing interests}
